BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-08-09 LabelStyles/skeleton-customfont.Rmd
working on scope of users sentence/s

---
output: 
  pdf_document:
    latex_engine: xelatex # or lualatex
    keep_tex: true
params:
  Collection_number: Collection_number
geometry: paperheight=4in,paperwidth=4in,margin=0.1in
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{setspace}
  - \usepackage{fontspec}
  - \setmainfont{Georgia}
  - \newfontfamily\couriernew{Courier New}
---

@@

\couriernew{`r writer(record[['Habitat']])`. `r record[['physical_environ']]`}
Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

>>>>

---
output: 
  pdf_document:
    latex_engine: xelatex # or lualatex
    keep_tex: true
params:
  Collection_number: Collection_number
geometry: paperheight=4in,paperwidth=4in,margin=0.1in
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{setspace}
  - \usepackage{fontspec}
  - \setmainfont{Georgia}
---

@@

`r writer(record[['Habitat']])`. `r record[['physical_environ']]`  
Veg.: `r species_font(record[['Vegetation']])` `r associates_writer(record[['Associates']])`
`r writer(record[['Notes']])`  
\endgroup

### 2025-08-09 LabelStyles/skeleton-maps.Rmd
working on scope of users sentence/s

---
output: 
  pdf_document:
    latex_engine: xelatex # or lualatex
    keep_tex: true
params:
  Collection_number: Collection_number
geometry: paperheight=4in,paperwidth=4in,margin=0.1in
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{setspace}
  - \usepackage{fontspec}
  - \setmainfont{Georgia}
---

@@

```{r load data}
local <- file.path('~', 'Documents', 'assoRted', 'Barneby_Lives_dev', 'LabelStyles')

record <- read.csv(file.path(local, 'SoS-ExampleCollection.csv')) |>
  sf::st_drop_geometry() |>
  data.frame() |>
  dplyr::filter(Collection_number == params$Collection_number) 
```

\begin{center}
\textbf{\Large `r writer(record[['Project_name']])`}
\end{center}
\begin{flushright}
\uppercase{`r record[['Family']]`}
\end{flushright}
\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
`r writer_fide(record)`
\normalsize
\endgroup

\vspace*{\fill}
\begingroup
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_uncertainty']])`).

@@

\vspace*{\fill}
\begingroup
`r collection_writer(record)`
\endgroup

>>>>

---
output: pdf_document
params:
  Collection_number: Collection_number
  imagepath: imagepath
geometry: paperheight=4in,paperwidth=4in,margin=0.1in
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{setspace}
---

@@

```{r load data}
record <- collection_examples |>
  dplyr::filter(Collection_number == params$Collection_number) |>  
  sf::st_drop_geometry()

imagepath <- params$imagepath
```

\begin{center}
\textbf{\Large `r writer(record[['Project_Name']])`}
\end{center}
\begin{flushright}
\uppercase{`r record[['Family']]`}
\end{flushright}

\noindent
\begin{minipage}[t]{0.78\textwidth}\vspace*{0pt}

\begingroup
\large
`r writer(paste(record[['Genus']], record[['Epithet']]), italics = TRUE)` `r writer(record[['Binomial_authority']])` `r writer(record[['Infrarank']])` `r writer(record[['Infraspecies']], italics = TRUE)` `r writer(record[['Infraspecific_authority']])`  
`r writer_fide(record)`
\normalsize
\endgroup

\vspace*{\fill}

\begingroup
`r record[['Gen']]`. `r writer(record[['Site']])` `r record[['latitude_dd']]` `r record[['longitude_dd']]` (`r record[['Datum']]` `r writer(record[['Coordinate_Uncertainty']])`).

@@

\vspace*{\fill}
\begingroup
`r collection_writer(record)`
\endgroup
\end{minipage}%
\hfill
\begin{minipage}[c]{0.18\textwidth}\vspace*{0pt}
\hspace*{4mm}% left margin
\centering
\includegraphics[width=\linewidth,height=0.66\textheight,keepaspectratio]{`r imagepath`}
\end{minipage}

convert -density 300 Molecular_nets-crop.pdf -quality 100 \
        -gravity West -background white -splice 100x0 \
        \( -background transparent -fill black -pointsize 12 \
           label:"Time within Season" -rotate -90 \) \
        -geometry +0+250 -composite Molecular_nets-crop-labelled.png

### 2025-08-09 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
working on scope of users sentence/s

>>>>

- User groups 
  - Academia
    - Botanists (floristics, inventory work)
    - Ecology (community ecologists)
  - herbaria personnel

We argue that the original collectors are the most qualified individuals to perform quality control checks and that BarnebyLives allows them to assume that responsibility in a relatively fast and streamlined format
While we largely highlight the usage of BarnebyLives in the context of herbaria, it's original use case was for natural resource management workers (e.g. US Forest Service, heritage programs, natural history surveys), and graduate students in ecology and conservation (e.g. inventory, and community ecology work).

We believe that these 
additional uses cases exist in domains where users seldom interface with curatorial staff, such as
